Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-15 tex/paper1/paper1.tex
adding in extra columns to results table
edits to the paper, improvements to plots

\section{Observations}\label{sec:obs}
AIA observes images of the Sun in multiple wavebands simultaneously
and continuously, at high cadence (12 seconds) and at high spatial
resolution (0.6 arcseconds per pixel at the Sun).  These data enable
detailed comparisons between phenomena seen in multiple wavebands, and
are therefore ideal for assessing the frequency content of the solar
atmosphere.  The data was acquired using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data in the time range 2012-09-23 00:00 - 06:00 UT, at
the full 12 second cadence, in the 171\AA\ and 193\AA\ wavebands is
used.  These wavebands were selected because previous studies in
similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
coronal oscillations.  The cutout of the Sun selected covers two
adjacent $\beta\gamma$ regions NOAA AR 11575 and AR 11577.  This
cutout was selected for two reasons.  First, it is quiescent in that
there were no X-ray flares or other large-scale disturbances (for
example, filament eruptions or rearrangments of long bright coronal
loops) over the spatial extent of the cutout within the time range
(Figure \ref{fig:loc171193}).  Therefore, any variations in the plasma
properties cannot be ascribed to large-scale disturbances.  Second,
the selected cutout region contains a sunspot, and sunspots are known
to be locations over which three minute oscillations have been
detected by other instruments \citep{2002A&A...387L..13D}.

@@

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

@@

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\delta$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  \\
                & & & & & & & \\

moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$  \\
                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$  \\
                & & & & & & & \\

quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$  \\
                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$  \\
                & & & & & & & \\

sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$  \\
                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\end{deluxetable}

@@

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  Table \ref{tab:parameters} shows the fitted parameter values
and an error estimate for model $M_{2}$.  For details on the fitting
procedure, see Section \ref{sec:app:ind}.

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC).  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv  k\ln N -2 \ln L_{max}
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\triangle AIC =
AIC_{1} - AIC_{2}$ and $\triangle BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\triangle AIC, \triangle BIC$ express a preference for model 2
over model 1 \citep{2007MNRAS.377L..74L, WICS:WICS199}.

Using both the AIC and the BIC, Model 2 is overwhelmingly preferred to
Model 1 (see Figure \ref{fig:fit171193}). Table \ref{tab:parameters}
gives the parameter estimates and 68\% credible intervals of the
parameter values.  The power law indices for all regions and both
wavebands lie in the range 1.8 to 2.3, although there is no
consistency between one waveband and another.  For example, the
171\AA\ and 193\AA\ loop footpoint results both have the same power
law index, but the other regions do not.  However, it should be noted
that there is no {\it a priori} reason why the power law indices for a
region seen in two different wavebands should be the same.  This is
because each waveband is designed to examine different features on the
Sun in broadly different temperature ranges, and may be imaging very
different physical processes: hence, the emission seen in one waveband
need not have the same statistical properties as any other.

>>>>

\section{Observations}\label{sec:obs}
AIA observes images of the Sun in multiple wavebands simultaneously
and continuously, at high cadence (12 seconds) and at high spatial
resolution (0.6 arcseconds per pixel at the Sun).  These data enable
detailed comparisons between phenomena seen in multiple wavebands, and
are therefore ideal for assessing the frequency content of the solar
atmosphere.  The data was acquired using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data in the time range 2012-09-23 00:00 - 06:00 UT, at
the full 12 second cadence, in the 171\AA\ and 193\AA\ wavebands is
used.  These wavebands were selected because previous studies in
similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
coronal oscillations.  {\bf The cutout of the Sun selected covers a single
$\beta\gamma$ active region, NOAA AR 11575}.  This cutout was selected
for two reasons.  First, it is quiescent in that there were no X-ray
flares or other large-scale disturbances (for example, filament
eruptions or rearrangments of long bright coronal loops) over the
spatial extent of the cutout within the time range (Figure
\ref{fig:loc171193}).  Therefore, any variations in the plasma
properties cannot be ascribed to large-scale disturbances.  Second,
the selected cutout region contains a sunspot, and sunspots are known
to be locations over which three minute oscillations have been
detected by other instruments \citep{2002A&A...387L..13D}.

@@

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 1575 and some surrounding area.
  \citep{2006A&A...449..791T}.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{{\bf The proportion of the number of pixels in each image
    that have a given Fourier power at some sample Fourier
    frequencies.  The left hand column gives results for AIA 171\AA,
    and the right hand column, AIA 193\AA.  Regions are indicated in
    each plot title.}}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

@@

\begin{deluxetable}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & 
\multicolumn{3}{c}{lognormal $G(\nu)$} & 
\multicolumn{2}{c}{ratio $P_{1}(\nu)/G(\nu)$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\delta$\tablenotemark{1}} &
\colhead{$\max$}          & 
\colhead{$\arg\max$ (mHz)}
\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  & & \\
                & & & & & & &   & & \\

moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & & \\
                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & & \\
                & & & & & & &   & & \\

quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$    & & \\
                & & & & & & &   & & \\

sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & &  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\tablenotetext{1}{Values are quoted in decades of frequency}
\end{deluxetable}

@@

\subsection{Results}\label{ssec:results}
Figure \ref{fig:fit171193} show the fit results of each model to the
data.  For details on the fitting procedure, see Section
\ref{sec:app:ind}.

The two models are assessed for how well they describe the data in two
different ways.

Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that model 2 loses less information compared to model 1,
leading to a preference for model 2 over model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).

The AIC reveals which out of a set of models is preferred.  It does
not give an assessment of the goodness-of-fit of each model.
Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is calculated for both models.

Table \ref{tab:parameters} gives the parameter estimates and 68\%
credible intervals of the parameter values for model $M_{2}$.  The
power law indices for all regions and both wavebands lie in the range
1.8 to 2.3, although there is no consistency between one waveband and
another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
both have the same power law index, but the other regions do not.
However, it should be noted that there is no {\it a priori} reason why
the power law indices for a region seen in two different wavebands
should be the same.  This is because each waveband is designed to
examine different features on the Sun in broadly different temperature
ranges, and may be imaging very different physical processes: hence,
the emission seen in one waveband need not have the same statistical
properties as any other.
